---
title: "Analysis of Simulation Distribution"
author: "Brady Chiu"
date: "May 2, 2016"
output:
  pdf_document:
    number_sections: yes
    toc: yes
    toc_depth: 4
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 4
---

# Intro

The purpose of this project is to analyze the ToothGrowth data in the R datasets package.

```{r message=FALSE, warning=FALSE, cache=FALSE, echo=FALSE}
knitr::read_chunk("../code/main.R")
```
```{r setup, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, include=FALSE}
```

# Data

```{r data_load, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, include=TRUE}
```

* We take a high level overview of our dataset  

```{r data_summary, message=FALSE, warning=FALSE, cache=TRUE, echo=TRUE, include=TRUE}
```

* We create a boxplot to see the impact of varying dosages of orange juice vs. vitamin C on tooth growth  

```{r data_boxplot, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, include=TRUE}
```

* We see tooth growth increases along with increased dosages of either orange juice or vitamin C  

# Analysis

## Supplement

* We conduct a t-test to determine if a statistically significancant difference exists between our supplments  

```{r ttest_supp, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, include=TRUE}
```

* Our p-value between 0.05 and 0.10 shows marginal statistical siginficance, with a 95% confidence interval that the differences is between -0.1670064 and 7.5670064  

## Dosage: 0.5 vs 1.0

* We conduct a t-test to determine if a statistically significancant difference exists between dosages of 0.5 vs 1.0  

```{r ttest_dose_1, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, include=TRUE}
```

* Our p-value < 0.05 shows statistical siginficance, with a 95% confidence interval that the differences is between -11.983748 and -6.276252

## Dosage: 0.5 vs 2.0

* We conduct a t-test to determine if a statistically significancant difference exists between dosages of 0.5 vs 2.0  

```{r ttest_dose_2, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, include=TRUE}
```

* Our p-value < 0.05 shows statistical siginficance, with a 95% confidence interval that the differences is between -18.15352 and -12.83648

## Dosage: 1.0 vs 2.0

* We conduct a t-test to determine if a statistically significancant difference exists between dosages of 1.0 vs 2.0  

```{r ttest_dose_3, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, include=TRUE}
```

* Our p-value < 0.05 shows statistical siginficance, with a 95% confidence interval that the differences is between -8.994387 and -3.735613

# Assumptions

Some assumptions we hold in order to form our conclusion(s) are:  

* Population is iid normal gaussian   
* Random samples were used for all treatments  

# Conclusion

* Suppment type has some effect on tooth growth
* Increasing dosage levels has a positive impact on tooth growth  

# Code
```{r setup, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r data_load, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r data_boxplot, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r data_summary, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r ttest_supp, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r ttest_dose_1, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r ttest_dose_2, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r ttest_dose_3, message=FALSE, warning=FALSE, eval=FALSE}
```